
%% Arrange all of this in a good structure linked to the thesis intro etc...
\chapter{Adoption challenges and unforeseen side effects of massive citizen experimentation systems}
-- other stuff we tried but didn’t work

ajkrjabwj


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Conclusion}
%"build theory, think expansively, and tackle broader conceptual issues, not (primarily) to reiterate the literal outcomes of your work.”-srk

Themes
\begin{itemize}
\item 1. improve techniques  -- how to teach better and more complex stuff
\item 2. improve systems -- how to bake these ideas in the interface and backend
\item 3. improve results -- how to scale beyond fun experiments
\end{itemize}

%todo-simplify future work and concerns
\section{Shortcomings / Challenges / limitations}
%"What were the challenges of this work? For example, the difficulty of gathering longitudinal data b/c people are tied to their email client. How would you recommend others address these challenges?" - srk
\begin{itemize}
\item is this really scientific work? what’s missing?
1. place-controlled blind exp \\
2. self-administration \\
3. difficulty of manipulation consistency 
---  causality (and ML)   
\item Use exsiting corpus of procedural learning -- wikihow provides a corpus -- how does this interface wiht expert patterns ideas
\item Engagement is hard man -- see msb write up -- show numbers of dropout etc..
\item worsened by making people work in lockstep --  difficulty of implementing on the ground - akshay roongta thesis -- Cultural effects in self organization of crowds?
\item hard to measure learning gains -- do people even learn?
\item dual objective systems

\end{itemize}

%%%%%%
\section{Implications}
%"If the world were to transform to rely heavily on your work, what broader technical and societal transformations would arise? How would your work scale? What would the social and technical challenges be? This might be a good place to connect your work to broader (relevant) writing on the role of technology in society"-srk
\begin{itemize}
\item personal intuitions provide one set of hypo generation -- others could be folk theories, data tracked from devices, observations, playing around with data using Vega-lite; ways to evaluate could be different too -- data analysiss
\item Also, what really makes you a scientist? -- how to enable deeper work in microbiome
\item Polio took such a long time from results to policy --  how to get citizens to create such knowledge -- link to health world
\end{itemize}


%%%%%%
\section{Systems/domains} 
%\section{New Systems? Other areas of application?}
% "where else could your techniques and insights apply? Think big."-srk

\begin{itemize}
\item We found that our approach works well for scineitifc experimentation; what about toher types of work and genre?
--talk about my procedural rules for writing papers or doing data science or activism \\
-- the challenge: proving that many other classes of work also fall in this category
--interpreting work around us a function of these techniques — individual production, peer reviews, and standard implementation
\item other medical/health domains -- This worked for microbiome due to three reasons: nascent, personal, motivating 
\item nursing and midwife programs
\item auto-generating galileo for different tasks
\item teaching machines using procedures rather than declarative knowledge -- where the traning data is procedures
\item Automation -- can we learn from the data that we have collected? -- a classifier or something else? -- optimize backend -- 
\end{itemize}

% fig: a set that shows many approaches for generating hypotheses and evaluating theories
%-- and says these systems are all waiting to be built


%%%%%%
\section{Patterns} 
%"What are the research issues for advancing and crystallizing patterns in this area?" - srk
\subsection{Theoretical Questions}
\begin{itemize}
\item link between procedural and conceptual learning
\item does this link to transfer learning? -- do people improve what they learn?
\item what do we know about tacit knowledge — expert knowledge  --- where is this useful? what kind of knowledge is this?
\item transfer learning --  "We instead need to transfer knowledge from diverse prior experiences when trying to learn new tasks. Transfer learning"
\item How much can you get done with procedural learning -- its limits?
\item new ideas about interfaces like ????
%     see email threads with tricia
\end{itemize}

%%%%%%
\section{Methods} 
%"Reflecting on the methods you employed – system building, studies, etc. What worked best? What effort was wasted? What things would you do differently? And what would you recommend (or not) to others? (This might go adjacent challenges.)" - srk




%%%%%%
\section{Behavior} 
%"what do you want to know about human behavior? For example, we know that most behavioral interventions (like exercising more) are tough to stick. Speculate beyond your data about behavior. Generalize. Make wild guesses. And think about what next steps would help you get to those." - srk


%%%%%%




1 .Framework: A different human-machine integration way 
--  that puts people in the driving category, supported by algo
