
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Conclusion}
%"build theory, think expansively, and tackle broader conceptual issues, not (primarily) to reiterate the literal outcomes of your work.”-srk
Drawing from empirical results, related work, and lessons from designing these systems, this chapter provides future steps along three themes: 1) building future system contributions, 2) identifying open questions for theoretical contributions, and 3) thinking through broader implications for computation in society.
%for designing new systems and for contributing novel theory. 

%%%%%%%%%%%%%%%%%%%%%%
\section{Systems/domains} 
% "where else could your techniques and insights apply? Think big."-srk
% fig: a set that shows many approaches for generating hypotheses and evaluating theories
%-- and says these systems are all waiting to be built

Domain experts make creative contributions like writing articles, curating museums, leading teams, and more. How might we enable a federation of novices to perform these activities? This dissertation demonstrates that procedural guidance works well for scientific experimentation. Could we develop such techniques to support other scientific activities? Useful techniques for just-in-time expertise include learning, community inputs, automation, and expert help. Which other genre of work and levels of contribution could this extend to? As in science, the number of experts in many domains is relatively small and their training relatively homogenous. 

%%%%%%%
%\subsection{Other domains that might benefit from procedural guidance}
\subsection{Deeper work: End to end scientific work}
%Social computing environments that model richer work in more domains using procedural support and roles
Experimentation forms a critical component of scientific work across many domains in the natural and behavioral science. Experimentation provides one method of enquiry; other ways to test hypotheses include conducting surveys, observational studies, and more. Furthermore, \textit{scientists} perform a range of activities including: 1) data analysis, and 2) comunicating the results (e.g. by writing a paper). One key challenge in such complex work is coming up with the initial design(s) that can be refined. 
%This dissertation demonstrates that procedural guidance enables people to transform an intuition to a structurally-sound experiment design.
%Starting with being able to understand and reason about the choices, there are many concrete activities that 

%e.g. finding participants was a challenge for experimenters - introduce gatherer here

% a virtuous (??) 
One popular process for writing includes creating an outline, converting the outline to a draft, and editing the draft. Previous research systems have supported people in editing papers~\cite{Bernstein2010a}. However, few tools support creating the outline and the first draft, arguably an onerous task. Research journals and conferences provide templates for formatting guidelines, but the argument and the authors need to generate the content and the argument. EteRNA participants used system-provided templates to write up their results and share with others~\cite{Lee2014}. How might procedural systems assist?
%see evernote

%multiple sources: experienced campaigners’ minds, books/tutorials, and internet posts. 
As is common for complex work, insights to write are distributed across people, static documents, and online resources. Experienced campaigners possess knowledge of the success criteria, mental scaffolds to help with writing, and access to other people to invite feedback on their work. Novices lack all these. Explicating experts' tacit knowledge and showing them to novices in the context of the work can be useful. To demonstrate the variance in the scientific writing process, let’s consider two contrasting examples: the methods section and the discussion section.

The methods section follows standard guidelines and many expert writers might find this to be easy to write up. However, writing the methods section is not straightforward for novices. The method section describes the study hypotheses, choices of measures and method of enquiry, and all relevant decisions taken while running the study. Furthermore, these details need to be mentioned in standard ways so others can understand and recreate these instructions. A procedural guidance system can rely heavily on templates in this case to ensure that novices don't commit standard \textit{mistakes}. The key insight here is for the system to support people in exploting the rather specific structure of the methods section.

The discussion section is far less templated though. The discussion section needs to bring together the ideas presented in the paper, the methods, and the results. In doing so, the discussion section needs to link ideas from multiple sections of the paper: claims about the novelty of the work, ways in which this work extends current enquiry, the actual results and how they deviate from the expected results, and the new questions created by this enquiry. A procedural guidance system for writing the discussion section can use multiple techniques; it can 1) identify the research question; 2) use rubrics to prompt the writer to reflect on their claims; 3) show examples from other discussion sections to show how to write specific portions; and 4) use checklists and peer feedback to improve clarity. The key insight here would be to help people explore all the options or questions to answer in the discussion section.

Such suggestions are preliminary; this dissertation's experience strongly suggests rapid iterations using pilots to understand the success and failure of different techniques. 
%The difference between domains differences too and it becomes interesting to note how this might shake out — that is what makes this research exciting.

\subsection{More domains for citizen-led scientific investigations}
-- measures change: self-reports, objective data 
-- process change: domain-specific
-- make it easier for other domain experts to use (co-design)

This dissertation used microbiome research as a petri dish because it’s nascent, personal, and motivating. Health related fields with devoted communites are a good match; these include nutrition, brain zapping, and more. However, the techniques develoepd in this disseration might not apply directly: different fields have widely accepted protocols of scientific research that might not be obvious to an outsider. Systems for these domains needs to provide appropriate rules and constraints that meet the objectives and processes fo these fields. E.g. tDCS folks are interested in testing whether brain zapping improves cognitive performance. The system can support people in using standard metrics and implementation. Another domain of enquiry is cultural psychology: people have theories about their (and others') behavior and research is limited~\cite{Henrich2010a}. Between-subjects experimentation might not be the most appropriate method of enquiry; observational studies might be more appropriate.
%Thinking more broadly, scientific work is not the only domain of application for this work — art (crowd art) can also learn from procedural rules [jennifer jacobs procedural art work] because it shares three features with our work: xx, yy, and zz.There are limits too: 1) when people do not have relevant expertise or when teaching them takes a lot of effort — consider journalism; 2)  when people don’t stand to gain?; 3)  when different people don’t bring in different expertise

%%%
\subsection{Designing efficient procedural support}
%highlight open questions?
%Procedural support provides a remixed version of computational thinking. 
Three questions

Computational problem-solving focuses on four key processes: abstraction, decomposition, generalization, and pattern matching~\cite{Wing2006}. With procedural guidance systems, the key difference is \textit{who} performs the work in these phases. For traditional computational problems, the (algorithm) designer performs these steps and implements them in the software. For a broad class of problems, a new \textit{learning} approach is popular: the designer decides the input and output specifications and provides the data; the machines' underlying structures perform the four phases independent of the designer. The trouble with computer procedures is that are interpreted literally; people are wiser. 

For complex socio-computational problems, the four phases might be implemented by different groups: the system designer might abstract the problem to a known class, provide decomposition and computational support using the system while people might perform open-ended tasks of generalization and pattern matching. This approach reconsiders procedures as instructions interpreted by machines \textit{and} people.
%  read computational thinking

\subsubsection{Integrating procedural support for your task}
%this heading is kinda useless
Based on this dissertation's struggles and results, we see the following process for how to integrate procedural guidance for a complex activity.
% (add figure)
\begin{itemize}
\item Examples, checklists, and templates provide procedural support: Procedural guidance works well when the sub-examples provide a direct link to the overall picture (e.g. hypo vs exp design).  Multimodal interactions for one or more of these can be useful too: e.g. people could see JIT videos of experts' work to draw inspiration rather than just looking at a final output. A key responsibility of the system is to handle the interaction between subparts or  provide examples of the sufficient abstraction; tackling all cases might be difficult. Dividing a complex artifact into specific subparts is difficult and requires starting from "good enough" places rather than providing perfect examples etc. The challenge is also of correctness: how do you teach complex ideas without making them wrong. Choosing appropriate examples etc is important.
\item People identify: People are good at identifying than generating~\cite{Stahl2006}. With procedural support, people aren’t blind users of the system but they actively translate what’s provided to them and do it back. Consequently, the support needs to be simple enough for the users to understand -- for novices, this might mean using simpler terminology. 
\item People transfer these ideas to their work/domain: To make the links concrete, the examples should be specific. To reduce the load of transfering the ideas, the support should be provided in-situ. Consequently, people will struggle when understanding procedural support itself takes effort or when the examples/checklists are too big or when this still requires expertise. 
\item Reviews from others: This should be complementary to the designer's work.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%
\section{Patterns} 
%"What are the research issues for advancing and crystallizing patterns in this area?" - srk
%     see email threads with tricia
How can computational systems reify different work environments for people to participate in personally meaningful scientific work? Answer this question requires aswering many research questions.

\subsection{Where does procedural support come from}
%Putting the knowledge together?
Many heterogenous resources---documents, experts, prior research artifacts---provide useful procedural guidance system. This dissertation employed many of these and found that each option provides different trade-offs.

\begin{itemize}
\item Static documents such as introductory books\\
Books aimed at novices provide a great resource to bootstrap procedural guidance. The systems described in this dissertation liberally used insights from multiple books including Martin’s Designing psych experiments~\cite{Martin2007} and the Blue book for social computing~\cite{Resnick2011}. Using books for introductory teaching provide multiple advantages: 1) they're intended for novices, therefore the information is basic; 2) the problems sets provide a corpus of common errors. However, these resources also suffer from three challenges. First, they focus on conceptual understanding rather than providing procedural workflows. Second, they might not provide appropriate \textit{chunking} size. For instance, implementing a book's insights line-by-line might lead to a highly bloated system that might not help the user arrange relevant material in useful, big-sized chunks. 
%Third, 
%Social computing systems will need to identify ways to convert learning resources (like books) to specific useful things in systems. Think 

%provide examples for all
%create a table for this
\item Procedural corpus from online fora, blogposts, wikihow, HCI artifacts\\
People provide copious details on topics of interest. On multiple online fora, people share details of their goals, their procedure, and even their evaluation of different techniques. E.g., wikihow provides a corpus of how to perform a wide range of activities from gardening to writing a letter. Comments on popular news articles (e.g. NYtimes) have plenty of details about people's attempts. Such approaches provide more practical knowledge that might be closely related to the author\textquotesingle s content. 

Prior research attempts have successfully draw insights to help people do things. Learnersourcing has demonstrated that learners can identify patterns that can be useful for others~\cite{Kim2015f}. Other work has demonstrated that conversations can be bootstrapped from fiction~\cite{fast2016empath}. Mining online forum data to identify procedural rules can reduce the designer's efforts in creating these procedures themselves. Finally, many HCI research systems for programming and witing identify key procedural insights that can bootsreap procedural systems. 
%While not procedural, prior research has demonstrated that people's beer preferences can be used to create a taxonomy of beer  [julian mcauley].
%crowdsourcing procedural rules

\item People \\
Expertise is a precious commodity; just teaching how to provide feedback takes plenty of effort from experts. For this dissertation research, microbiome experts were wary of providing feedback on the platform partly due to the time efforts needed. 

There are two ways to deal with this: First, active demonstration by experts where experts do something as part of their regular workflow and then ask people to follow. A step-by-step approach might be tailored to a person\textquotesingle s current bilities, ala zones of proximal development. Programming by demonstration makes one case for this. Second, passive tracking enables different activities performed by experts and then subsequent processing can draw rules form them. While working with people, being mindful of their time and effort is important.
%[??motif] 
\end{itemize}

Limitations: when the concept requires global awareness -- not for too "out there" ideas -- not all complex work have this breakdown e.g. collective activism - -when the software does not have a strong domain model

Like previous sections, this dissertation strongly recommends iterating with pilots to understand the success and failure modes of these resources and how to combine them in useful ways.
%-- pamhinds --
% zones of proximal development

\subsection{Learning tools for end-users to perform higher-order scientific work}
transfer learning -- does it happen

Learning has always been lifelong. Rapid change and the ready availability of online resources make it even more so. This dissertation seeks to place learning experiences at the right time for people to use them. This offers both theoretical and practical benefits. In the learning sciences, Bloom’s taxonomy shows a hierarchy of ways of engaging knowledge, from remembering facts to evaluating theories. Traditionally, this diagram invites a discussion of classroom learning objectives. Such an order implies a potential research trajectory. How might we leverage similarities between Bloom’s taxonomy of learning and the hierarchy of social computing roles? How might we design online learning environments for people to move their engagement with knowledge up the hierarchy? 

The interaction between procedural learning and social computing raises several key research questions: how do we integrate learning in systems? Do such approaches demonstrate learning gains? Consider the roles that emerged in the Gut Instinct platform. For instance, ideas from legitimate peripheral participation~\cite{Bryant2005} propose that engaging people in small tasks can assist in subsequently increasing their contributions. However, this idea has been tested for work that is less conceptual and less complex than experimentation. Does people's contribution across roles increase linerarly for complex work? Do different roles demonstrate different gains?
%expound on this

%todo- missing subsection about learning gains
%which examples are better than others


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods} 
%"Reflecting on the methods you employed – system building, studies, etc. What worked best? What effort was wasted? What things would you do differently? And what would you recommend (or not) to others? (This might go adjacent challenges.)" - srk
% read MSB - diss + the EA about social computing

%%
\subsection{Building a science of social computing systems}
Social computing systems leverage ideas from multiple disciplines and require substantial engineering. A science of such systems can support early-stage researchers in the face of high-barrier to entry and multiple points of failure. This dissertation identifies questions of prototyping, co-design, and emergent behavior as important issues and proposes a combination of theory, prototyping tools, and benchmarks. 

%simplify
%This section raises three questions: how do we design systems that are 1) quick to build, 2) that meet their objectives. Secondly, how can people engage with these systems: such that more people use them, and that these happen in collaboration with others. I also share ways to do this and provide examples.

%%%
\textbf{Prototyping}: How can we rapidly build, debug, and improve social computing systems? For instance, evaluating social computing systems is difficult: 1) there are multiple features (and related, multiple measures); 2) traditional HCI evaluation schemes are ill-suited; and 3) finding participants is a challenge.

%1 - many features
All three systems presented in this dissertation have multiple features. Traditional HCI interface research might suggest evaluating these features separately. Unfortumately, this is prohibitive: evaluating more requires more users and gerater effort from the designer(s). Social computing evaluation "requires" more holistic testing than usability or feature testing. Additionally, social computing systems typically enable people in performing specific tasks, the evaluation inherently judges co-creation between people and systems.

One approach might be to categorically separate measures for system evaluation (e.g. do people collaboratively create better questions using Docent?) from feature evaluation (e.g. does Docent‘s edit feature help people improve another user’s question). A clear separation might help system designers sort the evaluation components in order of importance, assign different quality thresholds (e.g. controlled experiments vs observational evaluation), and communicate overall evaluation effectively to the research community.
%combine with below

%1.5 - evaluation measures
%Identifying the key purpsoe of the social computing system. A \textit{successful} system balances an objective function across multiple factors: user longevity, activity, engagement, deeper work done not to mention qualitative measures like quotes etc. It can be easy to be lost among all these measures; worse, it might be possible to claim success
%However, despite all these activities, a designer still needs to identify specific measures. . 

%Focusing on just one metric is incomplete; however, claiming success based on any pick and choose of metrics (including hand-picked participant quotes -- provide all the quotes or provide none) seems intellectually dishonest too. This is the social computing version of p-hacking. I'll call this participant quote hacking. There needs to be stricter hypothesis-driven testing where people clearly lay out the intervention and the measure and identify others are side-issues. Consistent with recent thrust in social sciences, these hypotheses must be pre-registered (which means also write the scripts etc..). This key metric idea comes with the added advantage of focusing the designer's attention on one thing.

%Make measures about human activity, not the features. In social computing, the tech doesn't do it, but rather people do it. Example from gi: we tried testing for learning but failed and also realized that's not what people cared about -- so we threw it out and instead focused on one thing in subsequent iterations with hypothesis-driven testing. 

%2 - Pilot and evaluation process
%between-subjects experiment is the gold standard to evaluate but strict manipulation of one broad condition is difficult. -- mechanistic explanations are hard to find
%-- ask people -- foldit has already found that asking people how they do it is super useful
%-- build the system in a way that you can find out where the problem is. e.g. in galileo, we learnt that people drop off at the first step, but we still don't know whether it was because 
%My suggestion: ..... 

%3- participants
Every design-build-deploy cycle requires multiple iterations with groups of people - this has been the bottleneck in system development for this dissertation. How do we find people to pilot these sytems? Friends and labmates aren't good proxy. Personal and social relations might bias participation; moreover, they might they might know about the research. Paying crowdworkers doesn't work either because extrinsic motivation can lead to different results than intrinsic motivation~\cite{Chandler2013}. Furthermore, such users are not representative of the real people using the system.

One way to find to partner with organizations that care about the topic. This dissertation research leveraged participation from American Gut and multiple communites. Asking community leaders to be early users provides multiple advantages: 1) they provide a good proxy and adequate representation of the people; 2) typically, they have more experience with the community's working and goals; and 3) gatekeeping reduces chances of harm. However, this increases the workload for community leaders willing to help out; social computing system designers should create specific channels for such volunteers to provide useful feedback.
%other avenues like co-authorship should be considered
%what does this mean for the process of social computing 
%todo-see details from my lessons building social computing

%learning gains from the previous section

%also, use more surveys etc..

%%%
\textbf{Emergent behavior and limits}: How do interdependent, community-driven systems work in practice and how do participants self-organize? Principles derived from psychology, organizational behavior, and previous systems provide a starting point. However, the designer still needs to understand, select, and test multiple approaches before baking them in software, which necessitates further user-centered development and evaluation. Furthermore, small sample studies can also be poor predictors of emergent behavior in new systems. What roles emerge and how do we design for those?

The results of a traditional (not learning) algorithm provide a high degree of consistency when applied to different inputs: a binary search returns the location of the value searched for in a dataset; this consistent behavior is strictly a function of the algorithm; the data does not alter the efficacy of the algorithm. Results with people are less consistent. For instance, results are not even-keeled across users: some do more than others, many drop out, and take different roles~\cite{Bryant2005}. One approach would be to consider finer understanding of the results. Drawing inspiration from health sciences, looking at the outcomes clustered as positive and negative responses might be useful. E.g. rather than asking the question "Was this intervention useful?", it might be more useful to ask, "Did this intervention work for some poeple but not for others? If so, why?"
%4 - users -- what they did and how


%My suggestion: focus on human activity. another example: focusing on human activity also led me to find roles in different things that people did -- this was useful and might have been otherwise lost. 2) Also, conduct surveys etc. and ask them, 3) sometimes it's not about the system at all. people have other motivation.
%Finally, what are the limits to solving problems with social computing? 

%%%
\textbf{Co-design with other experts and users}: This dissertation features contributions from multiple communities—such as kombucha enthusiasts, Open Humans. The research papers feature 27 co-authors from five fields including microbiology, cognitive science, learning psychology, and systems. Many diverse efforts, including Precision Medicine Initiative (allofus.nih.gov), Zooniverse (zooniverse.org), and Foldscope Microcosmos (foldscope.com), might benefit from using this dissertation’s principles to diversify and deepen citizen contributions. However, building such a network requires effort that are tangential to research. How do experts across multiple domains contribute towards building systems that support domain-specific enquiry? 

Working with multiple domain experts brings great value and learning opportunities but also multiple challenges. It requires finding common ground and developing a shared vocabulary. One approach is to ground the conversation in prototypes invites specific feedback from domain-experts that helps the system designer draw higher-level principles. Less emails and Regular meetings~\cite{rocco1998trust} help catch early errors. For example, an early prototype with chat ideas floundered at the prototyping stage itself because experts mentioned that finding details in people's conversation will be expert time-intensive and they did not want to do that. However, building the system still needs work. Might there be ways to automatically bootstrap multiple prototypes for specific atomics tasks (asking questions, adding responses) that enable these conversations to be faster and more detailed as easy as templates? 
%Wat mgiht be a temlated way to develop social computing systems? Does it need to be digital? Could experts paper prototype different parts of the system? (papier machie system)

%%
%Furthermore, many collaborative projects lead to novel opportunities and transfer of ideas in all directions. how do we make this more systematic? Gut Instinct collaborators have brought their diverse insights to human-computer interaction work; they have also taken HCI techniques home. Some of them now use needfinding and low-fidelity prototyping techniques before beginning complex software development. While these questions are difficult to answer in the abstract, creating ways for social computing researchers to share their ideas towards building such knowledge base can be super useful.    %https://en.wikipedia.org/wiki/$Co-production_(public_services)$
%How might systems support co-design by users?









%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Behavior} 
%"what do you want to know about human behavior? For example, we know that most behavioral interventions (like exercising more) are tough to stick. Speculate beyond your data about behavior. Generalize. Make wild guesses. And think about what next steps would help you get to those." - srk

I would argue that these systems are only as exciting as the behavior that people demonstrate. 

We want to understand people's behavior as well as improve it. 
%condense all to like two lines
%"insights on who participates, what motivates them to participate, and how they participate”.
%todo - organize in terms of research questions

%link these to the topics discussed above
Another conceptual question is understanding the limits to procedural work. Based on procedural support as described above, it has limitations as well. This approach will struggle when when the concept being studied requires global awareness which is a hallmark of complex work: the sum is greater than the parts.  While procedural support can scale well, it might struggle for too “out there” ideas.

It's also important to not all complex work have this breakdown. For instance, consider collective activism. — there’s no set way to do this. How will the roles and procedural support look like for activities that do not have templated format like between-subjects scientific experimentation?  what happens when software does not have a strong model of the domain or a "high-level" recipe that can be improved.
%when do different elements of procedural guidance become important - templates for methods and iteration for discussion


\subsection{Does active doing lead to different behavior}
This general idea of making tacit knowledge explicit is super cool even for people themselves. This knwoledge comes from behavior in parts and also shapes behavior in part. With active doing, will poeple update their beliefs and their actions? A deeper question is how does offline doing translate to online doing? Does it, even?

Do people think in more evidence-rich ways in other domains?

So, basiclly, is there transfer from the offline to the online world, and from one domain to another?

Does it make people understand scientific work better?

Supporting complex work will require more than basic platform building but actually tying in to the motivation that people have.

\subsection{How to get more diverse people to participate?}

Complementing Global Data Collection with *Global* Distribution of Expertise is a worthwhile goal. This dissertation believes in a future of equal opportunity among people and equal skills. When people use such systems, two possible concerns come up: they provide a skewed population of the globe, and they perform little and drop out a lot. Plenty's been said about the latter, so i'll focus on the former.

Most Gut Instinct participants are from rich educated countries: 80\% of Docent questions were from people in the developed world and all 3 experimenters had advanced degrees. To brush away the difference in participation would be intellectually dishonest. More needs to be done to make the system meaningful for more people and to reach out to them. 

\textbf{Accept the multiplicative (not additive) effect of technology [??toyama]} - Rich country people are more likely to have more friends who are educated and willing to help out. System like Gut Instinct assume that people around the world have useful insights to share from their experiences. The results show this to be true. When people from educated, rich countries use these systems, they draw more attention to their concerns feeding into a feedback loop. Owing to how systems are linked with each others, such effects are more multiplicative rather than additive.  Missing people not represented on the platform across the world have different ideas and insights. we are missing out on those. People have the context, we want techniques to build expertise in people [raghuram rajan]

These are the concerns but how can we mitigate these issues.

%\textbf{Design phase}: Involve more relevant users in the design phase.

\textbf{Culturally-agnostic and -sensitive incentive design}
%see my angry locals email about this thing
A lot of our understanding is based on people in WEIRD countries [??WEIRD]. Since psychology studies have built upon fundamental ideas tested with Caucasian students in 1960s, it’s difficult to assume these apply to everyone, and especially with these results being questioned. People across different cultures might be motivated by different factors. 

Drawing on different cultural norms is important. LITW research has demonstrated that people across cultures have different flavor for “good” webpage design. TeachAIDS example where culturally-sensitive design changed outcomes: using locally tailored videos and other examples changed this.

There are two general themes to enable this: find the common things across cultures, and amplify uniquely for different populations. For the latter, basically, identify what’s the reality for people around the world and link it up to real stuff going on all around. Which of these techniques works better in engaging and improving contributions from prople? that itself could be interesting? Are we mostly similar or are we mostly different?

Some ways to find common grounds that cut across culture include: 
\begin{enumerate}
\item Self-promotion is another: Furthering one’s professional career and spreading one’s name is always a motivation. Similar to how Lil Wayne came from mixtapes [??], comedian Bill burr from podcasts, Xxx from twitter and blogs [??], Yyy from live-streaming[??]? In all these cases, people demonstrated their expertise by sharing their work in the open territory. While open science advocates pre-registering hypotheses and sharing insights, it still seems focused on experts; can we link such work with people’s real needs. will we find a scientist like this? doing their work and putting it in the open territory.

While other research like Crowd Research has looked at how other options like going to grad school is motivating, using “limited seats” opportunity to increase competition is not what i’m excited in. While creating an artificial sense of scarcity might be fine somewhat, it's not great. 
% what are other such research doing?

\item Temporal motivation and more: Motivation is not just cultural, it can also be temporal. E.g. When looking to draw broad participation on a topic like a disease, awareness months provide a natural time for people to be engaged in this, as demonstrated by the success fo ALS water bucket challenge. This gives a sense of collective work that trascends particular identities hopefully.

\item {Motivation to learn: Provide link to experts}: People like listening to experts (add Rob image). This might be even more pronounced in places where experts are considered distant.

\item{Extrinsic motivation in small parts}
While the willingness to do something might be based on personal meaningful nature of the task, actually doing it is more complex. People lack the time/remuneration/resources to learn new things and implement them in their lives. Might payment help? Combine intrinsic with extrinsic motivation provides one way. Pay people to start using the system, receive feedback, then have them continue using it [??personal conversation: jen mankoff]. 
\end{enumerate}

%todo-see east vs west common themese
Identify what works in local cultures and amplify them online. Some ways to engage specific audiences: 
\begin{enumerate}
\item Understand the complex economic and social factors. E.g. in societies that are strictly hierarchical and place experts way above novices, novices might be more concerned about challenging experts. Just because it has been put online does not mean it’s useful. 
\item Runtime - collaborating with on-ground experts: work with on-ground agencies, 3) Groups with greater motivation — patients
\item Altruism: While some might be motivated by self-interest and money, others might want to help out. 

\end{enumerate}

\textbf{Task and System design: Take an end-to-end view}

The blue book provides a great guide for what needs to be done. Here are some more specific ideas from my work.

\textbf{Initiation: will they feel they *can* and want to contribute?} With novel systems like Gut Instinct, people might not know or believe that they have much to contribute. Make this explicit to them — show examples, maybe identity-specific. Plenty of research demonstrates that when people find themselves in the right photo, they do more. As this Soylent post demonstrates, people might have different ideas about this platform. Communicating what the platform does is important. Do people feel this is meaningful for them?

\textbf{Make it easier for people to find what to contribute to and how - pre-registration might help} Diversity in roles: Technical interventions are scalable, social interventions are powerful. people’s interactions must be designed so they know what to do when. This is important due to a large diversity of both knowledge and participation  (dropout to leaders). 
%Take an iranian example and fix it

\textbf{continued use: }:  Do people find this useful now that they use it? How might the system better meet their needs?


\textbf{Finally, link the thing back}: Linking back the results with what they did — and inviting feedback 
%maybe fig for this thing


%todo- overall, link this with socio-technical gap
Not all social computing systems have the same affordances. It depends on the task being performed. Do standard tricks apply? Finally, be aware of the things that are lost with domain-specific social computing. standard online engagement tricks apply less to online scientific experimentation. People find online platforms engaging when they have social experience, receive feedback, and show their personality (personalize their profile, share photos, or share other info). Sadly, these activities as part of participating in an experiment can reduce scientific validity by nulling the independence of data assumption. What kinds of online interactions can be allowed (and tracked for conformity checks later) while still participating in an experiment? Future work can study that.

Many people around the world do not have access to education and other systematic resources. In the absence of functional institutions in many parts of the world (including huge swathes of “developed” countries), internet systems become even more important:  do they focus attention on questions of personal meaning that can improve one’s life or do they take attention and other resources away?

%Take for example the case of MOOCs and the stanford student who ranked 125 in the class after all other students from places around the world.

%%%%%%%%%%%%
\section{Implications}
%"If the world were to transform to rely heavily on your work, what broader technical and societal transformations would arise? How would your work scale? What would the social and technical challenges be? This might be a good place to connect your work to broader (relevant) writing on the role of technology in society"-srk

implications for social computing?
1. what it means for designing such systems and complex work
2. “how to eke out tacit knowledge from people"

\subsection{What does it mean to be an expert: doesn’t have to be solitary} 
What does it mean to be a scientist? While dictionary defines a scientist as “a person who is studying or has expert knowledge of one or more of the natural or physical sciences.”, it’s an overarching idea that includes a broad range of experts. 

For all their useful contributions, Gut Instinct users (exp designers, participants, hypotheses generators) cannot be considered scientists by me due to three reasons
1. people lack deeper, difficult to conceptualize skills:  even though people design and run an experiment, there’s many kinds of evaluation that’s missing — e.g. figuring out the right research question given what’ known in the domain — linking to existing research
2. people play a specific role - there’s a gradation and specific skillsets — people prefer specific tasks how do we teach people these and build upon these. But this also opens up opportunities:  how can we get people to do more? Drawing on the ideas of legitimate peripheral participation, getting people started on one small thing can help them with the other thing. However, is this always true? Typical demarcation of LPP has looked at different nature of tasks — edit, write, more; but most have still been in the realm of simple knowledge work: but why does this work and when does this break? This is a question for future study.
3. Science is terribly social [latour - use specific insight.] — those things are not baked in though and overarching views of science present it at this "aha moment by a lone genius" story. All the aha moments are so small and narrow that we cannot even imagine. Ideas are discussed over coffee, gained from talks, reading papers — it’s a really messy process that cannot be entirely translated to a template. People get ideas from their lifestyle and use them in research and vice-versa. Feynman won a nobel prize for a question he came across watching kids in a cafeteria. How do you create those serendipitous encounters?


Writing, like science, has this question: what does it mean to be a writer/scientist. What if someone else edits your paper or someone else actually runs the experiment? How do we allot credits in these cases. MSB has used credit allocation algorithms but where are they good and where do they fail. 

While history is ripe with visions of the lone warrior, reality is warmer to the idea of groups of people doing things. Complex work like science was considered a solitary endeavor, now its social. Some, like writing, are still considered solitary.

E.g. many scientists publish popular books in collaboration with ghost writers [?]; who is the writer in this case? This brings up the absurdity of using old school ideas for how things happen or at least how we increasingly observe things to happen. Unless a writer is handling everything pertaining to a book, Writing a book is a collaborative effort. There are reviewers who provide feedback, readers, publishers.. 

 -- young scientists need more time to master the growing body of knowledge that lies between them and the frontier of a field -- collaboration among scientists and novices

Also, roles come up normally/naturally in social computing — should these be linked to just participation on the platform or draw from other expertise things too?

Automatically converting to a paper — writing methods section with an eye on reproducibility
or using the procedural rules i have collected 

\subsection{What might be the role of experts in this new future?}

Expertise is a precious commodity; this dissertation did not use experts for feedback due to time needed and liability questions. However, there might be other ways in which experts can be involved. Experts have successful provided feedback [shepherd], built systems as designers, and more.. 

Similar to other domains like crowdfunding—where people (not VCs) fund startup ideas  and citizen science — balance of role division can change too. But it doesn’t necessarily need to be terrible for experts. Maybe experts can provide specific procedural rules of how they do things and people can follow that. One place to introduce this can be reproducibility of scientific research, using multimodal instructing using videos and audios and interfaces etc.. (btw, this is also an instance of how procedural rule might be useful).

Another way could be to involve citizens in expert work — one bottleneck that i’ve found is that experts need to recruit more people - find citizens to recruit others. 

People can also experiment and reproduce and provide inputs about mechanistic explanations (e.g. teasing apart why it does or does not work)

I see following ways for experts to contribute (see msb diss) — Quality control  and more.

But there are challenges too: Might experts nudge people into their own questions? or bias their doing by suggesting feedback?
    Involving experts while ensuring the bring useful knowledge but not the biases would be important. How do we do this? Experts might be more useful for structure/process oriented feedback while the domain knowledge could still be provided by standard resources. Might working with novices help experts uncover their blind spots?

%implications for the individual, the community, and machines -- challenges, potential ways, etc... -- atoms, bits, culture
   % link to CBPR and community-led research


\subsection{Folk theories are relevant in many domains}
%and learning interfaces
Where else might folk theories be relevant?
fix the gap between citizens and experts

With our current times of fire and attack on truth, we are seeing an end ot the quest for an objective reality. Building a bridge between institutions and people’s lived experiences is important — we have processes for these but it’s not clear these are working. While numbers and data provide the illusion of objectivity, it’s not necessarily true: what if the research question is biased, what if measures aren’t correct. 
%https://www.snopes.com/news/2019/10/10/facts-and-data-arent-enough-to-combat-fake-news/

The key challenges include: 1) where are these relevant and how? 2) how to do is in a humane and efficient manner

A burgeoning field is developing around folk theories for narrative economics, cultural psychology, and more… 
%what do we know about tacit knowledge — expert knowledge  --- where is this useful? what kind of knowledge is this?

%how to do this
Polio took such a long time from results to policy --  how to get citizens to create such knowledge -- link to health world. We already know the difficulty of collecting data on the ground [akshay roongta thesis] -- Cultural effects in self organization of crowds?

Here are some ways to proceed.

First, Collect folk theories across cultures and then compare them and ask people for mechanistic explanations: from people around the world by asking them to share theirs; what might this system look like: -- what would it enjoy. Perhaps a metric of identifying plausible candidates would be cool -- would majority vote be the best? we don't know… For instance, think about how different cultures think differently of food — beef, pork, and more — what effect does it have on their nutrition en masse?

personal intuitions provide one set of hypo generation -- others could be folk theories, data tracked from devices, observations, playing around with data using Vega-lite; ways to evaluate could be different too -- data analysis




%%%%%%
%\section{More} 


\section{Shortcomings / Challenges / limitations}
%"What were the challenges of this work? For example, the difficulty of gathering longitudinal data b/c people are tied to their email client. How would you recommend others address these challenges?" - srk
Is this really scientific work though? To be able to publish in a top-tier journal and to inform policy, the experiments would need to satisfy domain-specific rules. This would inform more specific rules around manipulation (rather than self-adminstering the intervention), use of placebo, and so on. We also find these to be useful avenues for further social computing use: enabling family members to administer the intervention based on reminders, or even enabling them to randomize that order... 
	Also minimal pairs and double blind -- how would you implement it socially without bias -- this trade-off between social trust and bias can be interesting -- wll it be like x or like y


%corporations have so many resources -- how do we do this?
%	engagement metrics implemneted by people


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%From Data to knowledge to wisdom
This dissertation research provides a vision and prototype systems for complex work by drawing on insights from interactive systems, social computing, and learning theory  for enabling people to perform personally meaningful work. By doing so, this thesis intends to democratize expertise and provide ways to meaningfully embed computation in society. 
